The SMT Competition 2015--2018

### 2019-04-15 2018/report/SMT-COMP.tex
resolved TODO 7

The \emph{raw benchmark score} of a solver is a quadruple $\langle
e, n, w, c\rangle$, with
\begin{itemize}[noitemsep]
  \item \makebox[5em][l]{$e \in \{0, 1\}$} number of erroneous results (usually~$e = 0$)
  \item \makebox[5em][l]{$0 \leq n \leq N$} number of correct results (resp.~\emph{reduction} for the \ucoretrack)
  \item \makebox[5em][l]{$w \in [0,T]$} wall-clock time in seconds (real-valued)
  \item \makebox[5em][l]{$c \in [0, 4T]$} CPU time in seconds (real-valued)
\end{itemize}
\noindent
For the \maintrack and \apptrack,
$N$ is defined as the number of {\tt check-sat} commands, and
$n$ is defined as the number of correct results.
For the \ucoretrack, $N$ is defined as the number of named top-level assertions,
and $n$ is defined as the \emph{reduction}, i.e., the difference between $N$
and the size of the unsat core.

>>>>

The \emph{raw benchmark score} of a solver is a quadruple $\langle
e, n, w, c\rangle$, with
\begin{itemize}[noitemsep]
  \item \makebox[5em][l]{$e \in \{0, 1\}$} number of erroneous results (usually~$e = 0$)
  \item \makebox[5em][l]{$0 \leq n \leq N$} number of correct results (resp.~\emph{reduction} for the \ucoretrack)
  \item \makebox[5em][l]{$w \in [0,T]$} wall-clock time in seconds (real-valued)
  \item \makebox[5em][l]{$c \in [0, 4T]$} CPU time in seconds (real-valued)
\end{itemize}
\noindent
For the \maintrack and \apptrack, $e$ is the number of returned statuses that disagree with the given expected status (as described above, disagreements on benchmarks with unknown status lead to the benchmark being disregarded). For the \ucoretrack, $e$ includes, in addition, the number of returned unsat cores that are ill-formed or are not, in fact, unsatisfiable (as validated by a selection of other solvers selected by organizers).

For the \maintrack and \apptrack,
$N$ is defined as the number of {\tt check-sat} commands, and
$n$ is defined as the number of correct results.
For the \ucoretrack, $N$ is defined as the number of named top-level assertions,
and $n$ is defined as the \emph{reduction}, i.e., the difference between $N$
and the size of the unsat core.
